Molecular Gas Kinematics and Star Formation Properties of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231

### 2017-01-21 WRITEUP/ms_apj/ms.tex
accepted version

\slugcomment{To be submitted to the ApJ}
\makeatletter
\renewcommand\normalsize{\@setfontsize\normalsize{10.56}{11.4}}
\makeatother

\citestyle{aa}
\shorttitle{Molecular Gas Dynamics in the Strongly-lensed Quasar Host Galaxy RXJ1131$-$1231}
\shortauthors{Leung, Riechers \& Pavesi}

@@

\title{Molecular Gas Dynamics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231}
\author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
and \ssim2\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of $\sim$19\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find lensing-corrected stellar and dust masses, an IR luminosity, and a
star formation rate of
$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim4\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{11}{8}\% which is higher
than the
local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

\defcitealias{Sluse03a}{S03}
The quasar RXS J113151.62$-$123158 (hereafter RXJ1131)
at $z_\textrm{s, QSO}$\eq$0.685$ \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
studying the evolution of molecular gas properties in quasar host galaxies and the
connection between SMBHs and their host galaxies at intermediate redshift
given its unique lensing configuration.
The stellar emission in the host galaxy of RXJ1131 is lensed into
an Einstein ring of $1$\farcs$83$ in radius
that is clearly separated from the quadruply imaged quasar emission \citep[hereafter C06]{Claeskens06a}.
The foreground lens is an elliptical galaxy at $z_\textrm{L}$\eq$0.295$ \citepalias{Sluse03a}.
\citet[][]{Reis14a} report a high spin parameter of $a$\,$\sim$\,$0.9$ for the moderate-mass black hole in RXJ1131 \citep[$M_{\rm BH}$\eq$8$\E{7}\Msun;][]{Sluse12a},
with an intrinsic bolometric luminosity of $L_{\rm bol, X}$\eq$1.3$\E{45}\, ergs\,s\pmOne \citep{Pooley07a}.

@@

\section{Observations} \label{sec:obs}
\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
at the $\nu_{\rm LO}$\eq139.256\,GHz
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

\subsection{CARMA \cco}
Observations of the \cco rotational line in RXJ1131
($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz
were carried out with the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers)
in the D array configuration on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions.
This resulted in a total on-source time of 2.94 hours after flagging poor
visibility data.
The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a
spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks.

The \ncode{miriad} package was used to calibrate the visibility data.
The calibrated visibility data were
imaged and deconvolved using the CLEAN algorithm with ``natural'' weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 (PA\,=\,8\degr) for the lower sideband
image cube. The final rms noise is $\sigma$ = 13.3 mJy beam$^{-1}$
over a channel width of 25\,MHz. An rms noise of
$\sigma$\,=\,0.83\,mJy\,beam\pmOne is reached by averaging over the
line-free channels in both sidebands.

@@

\section{Results} \label{sec:results}
\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission toward the background source in the PdBI data
at $\gtrsim$\,27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
0.6537\,$\pm$\,0.0005. The emission is spatially and dynamically resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{f1.eps}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission toward RXJ1131, with a spectral resolution of
21.5\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
The velocity scale is with respect to $z$\,=\,0.6537, which is approximately the line center
considering the asymmetry resulting from differential lensing.
A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
\end{figure}
\vspace{.2em}
We construct a zeroth order moment map, red/blue channel maps, and
first and second moment maps, as shown in \Fig{CO21mom},
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are produced using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity map.

The deconvolved source size FWHM obtained by fitting a two-dimensional Gaussian to the integrated line map in
the image plane
is 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
and thus, the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as a two-dimensional
Gaussian;
the fit recovers the line intensity enclosed by the emitting
region, therefore we take this as an estimate on the full extent of the lensed
emission. On the other hand, if we assume that the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \nir
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein ring'' and
the lensed knots (see \Fig{CO21mom}).

\begin{figure*}[!htbp]
\hspace{0.5em}
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{f2a.eps}
\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{f2b.eps}
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{f2c.eps}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
image.
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
are extracted by integrating over $v$\,$\in$[0, 409] \kms and $\in$[$-$325,0] \kms, respectively.
The contours in both top panels start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
and
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}

@@

\subsection{\cco Emission}
We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim5\sigma$ significance.
The spectrum is shown in \Fig{co32spec} and appears to be consistent with a
double-peaked profile. We estimate a line intensity of
35.7\,$\pm$\,21.9 Jy\,\kms by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity ($\sim$700 \kms).
Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
magnified by the same amount, the measured line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.
Taking into account the large phase errors associated with \cco, this is consistent with
thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, but also
with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.

\begin{figure}[!htbp]
\includegraphics[width=0.455\textwidth]{f3.eps}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
The velocity scale is with respect to $z$=0.6537, which corresponds to the
dynamical center of the \bco line. The spectral resolution for \cco and \bco
is 35.8 \kms and 21.5 \kms, respectively.
\label{fig:co32spec}}
\end{figure}

\subsection{Continuum Emission}
No 1.5\,mm continuum emission is detected at the position of \cco
down to a 3$\sigma$ limit of 2.49\,mJy beam\pmOne.
This is consistent with the spectrum shown in \Fig{co32spec}.

We detect 2\,mm continuum emission at an
integrated flux density of
1.2\pmm0.2 mJy, with a peak flux of
$S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy (\Fig{cont}). Slightly extended emission
along the lensed arc is also detected.
This suggests that we detect emission in both
the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in the $uv$-plane to remove the unresolved part of the
emission, which we here assume to be dominated by the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). We therefore adopt
$S_{\nu}$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission towards
the background galaxy (RXJ1131).
The quoted uncertainty is from the flux measurement in the residual map and does not account for that in the de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
We report the peak flux in the original map
($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy, which
is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.

\begin{figure}[!htbp]
\includegraphics[trim=12 27 0 1, clip, width=0.475\textwidth]{f4a.eps}
\includegraphics[trim=10 5 0 0, clip, width=0.4695\textwidth]{f4b.eps}
\caption{Top: overlay of the 2\,mm continuum emission on the optical image.
Bottom: overlap of the VLA 5\,GHz continuum emission on the optical image.
Contours in both images start and increment at steps of
$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne and
$\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne in the top and bottom panel, respectively.
The central crosses indicate the centroid of the foreground galaxy,
as detected in the optical image.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$ for
the PdBI observations (top), and
0\farcs5 $\times$ 0\farcs4 (PA = 0.18$\degr$) for
the VLA observations (bottom).
\label{fig:cont}}\vspace{0.51em}
\end{figure}

The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
jets and the core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc with their centroids
coincident with the optical emission from the quasar.
We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.024
for the foreground
galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.345
for the background galaxy by fitting a
power-law ($S_\nu \propto \nu^{\alpha}$) to the continuum emission at
5\,GHz and 2\,mm.

@@

\subsubsection{Gas Mass Fractions and Gas-to-dust Ratio}

>>>>

\slugcomment{Accepted to the ApJ}
\makeatletter
\renewcommand\normalsize{\@setfontsize\normalsize{10.56}{11.4}}
\makeatother

\citestyle{aa}
\shorttitle{Molecular Gas Kinematics of the Strongly-Lensed Quasar Host Galaxy RXJ1131$-$1231}
\shortauthors{Leung, Riechers \& Pavesi}

@@

\title{Molecular Gas Kinematics and Star Formation Properties of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231}
\author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile and a smooth source-plane velocity
gradient suggest that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
We also find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\eq(1.4\pmm0.3)\E{10}\,\Msun
and (2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
We find a lensing-corrected stellar mass of
$M_{*}$\eq(3\pmm1)\E{10}\,\Msun and a star formation rate of SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU,
corresponding to a specific SFR and star formation efficiency comparable to
$z$\ssim1 disk galaxies not hosting quasars.
The implied gas mass fraction of $\sim$18\pmm4\% is consistent with the previously-observed cosmic decline since $z$\ssim2. We thus find no evidence for quenching of star formation in RXS\,J1131$-$1231. This agrees with our finding of an elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} compared to the
local value, suggesting that the bulk of its black hole
mass is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

\defcitealias{Sluse03a}{S03}
The quasar RXS J113151.62$-$123158 (hereafter RXJ1131)
at $z_\textrm{s, QSO}$\eq$0.658$ \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
studying the evolution of molecular gas properties in quasar host galaxies and the
connection between SMBHs and their host galaxies at intermediate redshift
given its unique lensing configuration.
The stellar emission in the host galaxy of RXJ1131 is lensed into
an Einstein ring of $1$\farcs$83$ in radius
that is clearly separated from the quadruply imaged quasar emission \citep[hereafter C06]{Claeskens06a}.
The foreground lens is an elliptical galaxy at $z_\textrm{L}$\eq$0.295$ \citepalias{Sluse03a}.
\citet[][]{Reis14a} report a high spin parameter of $a$\,$\sim$\,$0.9$ for the moderate-mass black hole in RXJ1131 \citep[$M_{\rm BH}$\eq$8$\E{7}\Msun;][]{Sluse12a},
with an intrinsic bolometric luminosity of $L_{\rm bol, X}$\eq$1.3$\E{45}\, ergs\,s\pmOne \citep{Pooley07a}.

@@

\section{Observations} \label{sec:obs}

\subsection{CARMA \cco}
Observations of the \cco rotational line
($\nu_{\rm rest}$\,=\,345.79599\,GHz) towards RXJ1131 at $z_{\rm s, QSO}$\eq0.658
were carried out with the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers) in the D array configuration.
The line frequency is redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz at the quasar redshift.
Observations were carried out
on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions.
This resulted in a
total on-source time of 2.94 hours after flagging poor
visibility data.
The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a
spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks.

The \ncode{miriad} package was used to calibrate the visibility data.
The calibrated visibility data were
imaged and deconvolved using the CLEAN algorithm with ``natural'' weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 at a position angle (PA) of 8\degr for the lower sideband
image cube. The final rms noise is $\sigma$ = 13.3 mJy beam$^{-1}$
over a channel width of 25\,MHz. An rms noise of
$\sigma$\,=\,0.83\,mJy\,beam\pmOne is reached by averaging over the
line-free channels in both sidebands.

\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
towards RXJ1131
were carried out using the IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers).
Based on the CARMA \cco line redshift of $z_{\rm CO(3-2)}$\eq0.655,
the \bco line is redshifted to $\nu_{\rm obs}$\eq139.256\,GHz.
Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

@@

\section{Results} \label{sec:results}
\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission towards the background source RXJ1131 in the PdBI data
at $\gtrsim$\,27$\sigma$ significance. Based on this measurement, we refine the redshift of RXJ1131 to
$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\footnote{This redshift is derived by fitting a double-Gaussian to
the de-lensed spectrum (\Fig{delensed})
instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our
redshift determination
due to differential lensing (see \Sec{differential}).
}. The emission is spatially and kinematically resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is 20.3\,$\pm$\,0.6 Jy \kms.

\begin{deluxetable}{lcc}[!htbp]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{Observed Properties of RXJ1131 and its companion}
\tablehead{
\colhead{Parameter} &
\colhead{Unit} &
\colhead{Value}
}
\startdata
$z_{\rm CO(2-1)}$   &                          & 0.6541\pmm0.0002 \\ [0.5ex]
$I_{\rm CO(2-1)}$     & Jy\,km s\pmOne           & 20.3\pmm0.6 \\ [0.5ex]
$S_{\rm CO(2-1)}$\tna     & Jy km s\pmOne beam\pmOne & 8.12\pmm0.30 \\ [0.5ex]
FWHM$_{\rm CO(2-1)}$ \tnb & km s\pmOne               & 179\pmm9, 255\pmm28 \\ [0.5ex]
FWHM$_{\rm CO(2-1)}$\tnc        & km s\pmOne               & 220\pmm72 \\ [0.5ex]
$I_{\rm CO(3-2)}$     & Jy\,km s\pmOne           & 35.7\pmm6.9
\enddata
\label{tab:obsprop}
%\tablecomments{}
\tablenotetext{a}{Peak flux density in the intensity map.}
\tablenotetext{b}{From fitting a double Gaussian to the observed \bco spectrum (\Fig{CO21spec}).}
\tablenotetext{c}{From fitting a double Gaussian with a common FWHM to the de-lensed \bco spectrum (\Fig{delensed}).}
\end{deluxetable}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{f1.eps}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission towards RXJ1131, with a spectral resolution of
22\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
The velocity scale is with respect to $z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
the de-lensed line profile (\Fig{delensed}).
A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
\end{figure}

We construct a zeroth order moment map, red/blue channel maps, and
first and second moment maps, as shown in \Fig{CO21mom},
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are produced using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity map.
Observed properties of the \bco emission line are summarized in \Tab{obsprop}.

The deconvolved source size FWHM obtained from fitting a single two-dimensional Gaussian
to the integrated line emission in the image plane yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,
which is consistent with that obtained by visibility-plane fitting within the uncertainties.
Since the spatial distribution of the observed CO emission is unlikely to be fully described by a simple Gaussian
and appears to be a superposition of at least two components (top left panel of \Fig{CO21mom}),
we also fit two Gaussians to the intensity map.
This yields deconvolved source sizes of
3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, separated by $\sim$2\farcs2 in RA and $\sim$1\farcs7 in Dec.
The deconvolved source sizes of both models suggest that the gravitationally lensed CO emission is more extended
than the optical
``Einstein ring'', which has a diameter of $\sim$3\farcs6
(i.e., the ``Einstein ring'' formed by CO emission is likely to have a larger diameter compared to the optical one).
This is consistent with the centroid position of the redshifted emission, which is along the quasar arc seen in the optical image,
and the blueshifted emission, which is offset further to the SE (top right of \Fig{CO21mom}).
Therefore, the CO-emitting region in RXJ1131 is likely to be more extended than its stellar and quasar emission.

\begin{figure*}[!htbp]
\hspace{0.5em}
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{f2a.eps}
\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{f2b.eps}
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{f2c.eps}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
image.
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.
The contours in both top panels start at 3$\sigma$ and increment in steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
and
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}

@@

\subsection{\cco Emission}
We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim$\,5$\sigma$ significance.
The \cco spectrum appears to be consistent with a double-peaked profile, as shown in \Fig{co32spec}, where
we over-plot spectra of the \bco and \cco lines.
We extract the peak fluxes and their corresponding uncertainties for the blue and red wing independently.
We find a peak line flux of 5.13\pmm1.43 Jy\,\kms beam\pmOne for the blue wing, indicating a $\gtrsim$3$\sigma$ detection for this component alone, and a peak line flux of 11.45\pmm1.99\,Jy\,\kms beam\pmOne for the red wing,
indicating a $\sim$\,6$\sigma$ detection.
We measure a line intensity of 35.7\,$\pm$\,6.9\,Jy\,\kms (\Tab{obsprop}) by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity.

Assuming that the spatial extent of \bco and \cco is similar and therefore the emission is
magnified by the same amount, the measured line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.78\,$\pm$\,0.37.
The quoted error bar is derived by adding the uncertainties associated with the CO line intensities
and those from absolute flux calibrations in quadrature.
This brightness temperature ratio is consistent with
thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, Riechers11b, CW13}, but also
with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13, Daddi15a}.

\begin{figure}[!htbp]
\includegraphics[width=0.455\textwidth]{f3.eps}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
The velocity scale is the same as in \Fig{CO21spec}.
The spectral resolution for \cco and \bco
is 36 \kms and 22 \kms, respectively.
\label{fig:co32spec}}
\end{figure}

\subsection{Continuum Emission} \label{sec:deblend}
No 1.4\,mm continuum emission is detected at the position of \cco
down to a 3$\sigma$ limit of 2.49\,mJy beam\pmOne.
This is consistent with the spectrum shown in \Fig{co32spec}.

We detect 2.2\,mm continuum emission at an
integrated flux density of
1.2\pmm0.2 mJy, with a peak flux of
$S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy (\Fig{cont}).
Slightly extended emission
along the lensing arc is also detected.
This suggests that we detect emission in both
the foreground and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in the visibility-plane to remove the unresolved part of the
emission, which we here assume to be dominated by the foreground galaxy. The emission
in the residual map coincides spatially with the lensing arc. We measure a flux density
of $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy for this residual component.
This flux density is consistent with
the difference between the integrated and the peak flux density measured in the
original continuum map ($\sim$0.4 mJy).
We therefore adopt $S_{\nu}$\eq0.39\pmm0.12 mJy as the best estimate for the 2\,mm continuum flux of
the background galaxy (RXJ1131).
We here quote a conservative error bar, which is derived by adding the uncertainty
associated with the flux density of the
point-source model ($\delta S_{\nu}$\eq0.088\,mJy) with
that of the peak flux in the residual map (0.08\,mJy)
in quadrature. We caution that this does not account for the systematic uncertainties of the
de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
We report the peak flux in the original map
($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy, which
is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.

\begin{figure}[!htbp]
\includegraphics[trim=12 27 0 1, clip, width=0.47\textwidth]{f4a.eps}
\includegraphics[trim=10 5 0 0, clip, width=0.47\textwidth]{f4b.eps}
\caption{Top: overlay of the PdBI 2\,mm continuum emission on the optical image.
Contours start and increment in steps of
$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne.
Bottom: overlay of the VLA 5\,GHz continuum emission on the optical image.
Contours correspond to $\pm2^n\sigma$, where
$\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne
and $n$ is an integer running from 2 to 5.
Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$ significance.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$ for
the PdBI observations (top), and
0\farcs5 $\times$ 0\farcs4 (PA = 0.18$\degr$) for
the VLA observations (bottom).
\label{fig:cont}}\vspace{0.51em}
\end{figure}

The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
jets and the core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc with their centroids
coincident with the optical emission from the quasar.
We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.02\pmm0.07
for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.35\pmm0.21
for the background galaxy by fitting
power-laws ($S_\nu \propto \nu^{\alpha}$) to their continuum fluxes at
5\,GHz and 2\,mm.
The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \citep[$\alpha$\ssim$-$0.7; e.g.,][]{Andreani93a}. This likely suggests
that at least a fraction of the observed 2\,mm emission arises from thermal dust emission.
This spectral slope would be even shallower
if the background source contributes to the unresolved fraction of the
2\,mm flux.
In this case, the 2\,mm flux of the foreground galaxy would be lower than the value reported here and
lead to a slope steeper than $\alpha^{\rm 2mm}_{\rm 6cm}$\ssim$-$0.02, which is flatter than
that typical of elliptical galaxies.
Assuming a spectral slope of $\alpha$\ssim$-$0.7 to account for synchrotron radiation in RXJ1131, we expect
a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm.
The flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy therefore likely arises due to thermal dust emission.

@@

\subsubsection{Gas Mass Fractions and Gas-to-dust Ratio} \label{sec:frac}
